\documentclass[11pt,twoside,a4paper]{article}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage[pdfstartview=FitH,pdfpagemode=UseNone]{hyperref}
\usepackage[letterspace=40]{microtype}

\usepackage{a4wide,times}
\usepackage{graphicx}
\usepackage{color}
\usepackage[section]{placeins}

\urlstyle{same}
\linespread{1.1}

\title{
  IN4086 Data Visualization\\
  Final Project Proposal\\
  ``Teamfight Classification in Defense of the Ancients 2 (DotA2) (cont.)''
}
\author{
    Tung Phan, ttphan, 4004868 \and
    Kevin van Nes, kjmvannes, 4020871
}

\begin{document}

\maketitle

For the final project we would like to expand our work on classifying and visualizing teamfights and their corresponding information. This work was started as part of Assignment 1 for this course. We were very enthusiastic about the assignment and we think it would be very interesting to see whether we could visualize other information with respect to teamfights.\\
\\
The tools we will use to reach this goal are the same ones we used for the first assignment: D3 and Javascript. We found that working with D3 helped a lot when it came to reading the data and visualizing it properly.\\
\\
We can not yet concretely define our deliverables. We want to do research into what kind of improvements can still be made to the existing results that we obtained from the first assignment. A general approach that we want to take is to visualize the data in such a way that both skilled and unskilled players can quickly retrieve information about the most interesting parts of a match. We had been thinking of adjustments such as being able to `slide' through a game and see teamfight locations (and possibly other things, such as objective control) throughout the game. We also want to create a way in which players can view and compare the teamfights of multiple matches at the same time. Lastly, if time allows it, we want to try and see if we can come up with interesting features and visualizations that do not directly involve teamfights. One thing we came up with was the visualization of objective control (killing creeps in the jungle, fighting near towers, etc.).\\
\\
We hope to see some more interesting results while working on this project!

\end{document}